---
title: "Module 3: Customer Segmentation"
author: "SPANDA"
date: "2025-06-06"
output: html_document
---

# Clustering Techniques

- K-means clustering
- Hierarchical clustering

# RFM Analysis

- Recency, Frequency, Monetary value

# Case Study: Segmenting Retail Customers

## Practice Exercise

1. Apply K-means clustering to a customer dataset.
2. Perform RFM analysis and interpret the segments.

## Practice with Imaginary Data

```{r}
# Create an imaginary customer dataset
set.seed(123)
customer_data <- data.frame(
  CustomerID = 1:30,
  Recency = sample(1:100, 30, replace = TRUE),
  Frequency = sample(1:20, 30, replace = TRUE),
  Monetary = sample(seq(100, 2000, by=50), 30, replace = TRUE)
)
head(customer_data)
```

### Example: K-means Clustering

```{r}
# Scale the data for clustering
customer_scaled <- scale(customer_data[,c('Recency','Frequency','Monetary')])
set.seed(123)
km <- kmeans(customer_scaled, centers=3)
customer_data$Segment <- as.factor(km$cluster)
table(customer_data$Segment)
```

### Try it Yourself
- Visualize the clusters using a scatter plot.
- Calculate average RFM values for each segment.
- Interpret the business meaning of each segment.
