---
title: "Module 8: Capstone Project"
author: "spanda"
date: "2025-06-07"
output: html_document
---

# Capstone Project: End-to-End Marketing Analytics

We'll use the `marketing_sample.csv` file for this project. Make sure this file is in your working directory.

## Step 1: Define a Business Problem

Suppose a retail company wants to improve its marketing campaign effectiveness. The business problem: "How can we identify which customers are most likely to respond to a new marketing campaign?"

## Step 2: Load and Explore Data

```{r}
library(readr)
library(dplyr)

# Load the data
df <- read_csv('../marketing_sample.csv')
head(df)
```

## Step 3: Data Cleaning & EDA

```{r}
# Check for missing values
colSums(is.na(df))

# Summary statistics
df %>% summarise(across(where(is.numeric), list(mean = mean, sd = sd)))

# Visualize distribution of Income
library(ggplot2)
ggplot(df, aes(x=Income)) + geom_histogram(binwidth=10000, fill='skyblue', color='black') + ggtitle('Income Distribution')
```

## Step 4: Segmentation Example (RFM)

```{r}
# Simple segmentation: High vs. Low Purchases
purchase_threshold <- median(df$Purchases)
df$Segment <- ifelse(df$Purchases > purchase_threshold, 'High Value', 'Low Value')
table(df$Segment)
```

## Step 5: Predictive Modeling

```{r}
library(caret)
set.seed(42)
df$Response <- as.factor(df$Response)
trainIndex <- createDataPartition(df$Response, p = .8, list = FALSE)
train <- df[trainIndex,]
test <- df[-trainIndex,]

model <- train(Response ~ Age + Income + Purchases + Campaign_Contacted, data = train, method = 'glm', family = 'binomial')
pred <- predict(model, test)
confusionMatrix(pred, test$Response)
```

## Step 6: Present Insights
- Summarize key findings from your analysis and model
- Make recommendations for the marketing team

# Your Turn
- Try different segmentation strategies (e.g., by age or income)
- Tune the model or try other algorithms
- Create visualizations to support your recommendations
