---
title: "Module 7: Advanced Topics"
author: "spanda"
date: "2025-06-07"
output: html_document
---

# Time Series Forecasting for Sales

We'll use the `marketing_sample.csv` file for all examples. Make sure this file is in your working directory.

```{r}
library(readr)
library(ggplot2)
library(forecast)
library(dplyr)

# Load the data
df <- read_csv('../marketing_sample.csv')
head(df)
```

## Time Series Forecasting Example

```{r}
# Simulate monthly sales
dates <- seq(as.Date('2024-01-01'), by = 'month', length.out = 10)
sales <- df$Purchases + sample(-1:1, 10, replace = TRUE)
time_series <- ts(sales, start = c(2024, 1), frequency = 12)

# Plot sales
autoplot(time_series) + ggtitle('Monthly Sales') + ylab('Purchases')

# Exponential Smoothing Forecast
fit <- ets(time_series)
forecasted <- forecast(fit, h=3)
autoplot(forecasted) + ggtitle('Sales Forecast')
```

# Text Analytics for Customer Feedback

## Sentiment Analysis Example

```{r}
library(textdata)
library(tidytext)
library(tibble)
library(stringr)

# Simple sentiment using Bing lexicon
df_reviews <- tibble(text = df$Review)
words <- df_reviews %>% unnest_tokens(word, text)
sentiments <- get_sentiments('bing')
words_sentiment <- words %>% inner_join(sentiments, by = 'word')
words_sentiment %>% count(sentiment)
```

# Machine Learning Applications in Marketing

## Churn Prediction Example

```{r}
library(caret)
set.seed(42)

# Features and target
df$Response <- as.factor(df$Response)
trainIndex <- createDataPartition(df$Response, p = .7, list = FALSE)
train <- df[trainIndex,]
test <- df[-trainIndex,]

model <- train(Response ~ Age + Income + Purchases + Campaign_Contacted, data = train, method = 'rf')
pred <- predict(model, test)
confusionMatrix(pred, test$Response)
```

# Your Turn
- Try forecasting with ARIMA or other time series models.
- Perform topic modeling on the review text.
- Build a recommendation system using the purchases data.
