---
title: "Module 1: Introduction to Marketing Analytics"
author: "SPanda"
date: "2025-06-07"
output: html_document
---

# Overview of Marketing Analytics

- What is marketing analytics?
- Importance in modern marketing
- Types of marketing data
- Key metrics and KPIs

## Practice Exercise

1. List 5 key marketing metrics relevant to your business domain.
2. Discuss how data-driven decisions can improve marketing ROI.

## Example Dataset

We'll use the sample CSV file (`marketing_sample.csv`) containing customer demographics, campaign responses, purchases, and review text. This file is available in your workspace.

```{r}
library(readr)
# Load the data
df <- read_csv('../marketing_sample.csv')
head(df)
```

## Example: Exploring Key Metrics

```{r}
# Total number of customers
num_customers <- length(unique(df$CustomerID))
cat('Total customers:', num_customers, '\n')

# Average sales per customer
avg_sales <- mean(df$Income)
cat('Average sales (Income):', round(avg_sales,2), '\n')

# Campaign response rate
response_rate <- mean(df$Response) * 100
cat('Campaign response rate:', round(response_rate,2), '%\n')
```

## Your Turn
- Try calculating other metrics such as customer retention rate, average purchase frequency, or customer lifetime value using the dataset.
- Reflect on how these metrics can inform marketing strategy.

